\begin{frame}
  I generally go by $\lambda x.x$, pronounced lambda x dot x though often
  shortened to lambda, and poxks on reddit. If you only have the slides, please
  find the accompanying lecture videos on my
  \href{https://www.youtube.com/user/Restrong}{channel} since the slides by
  themselves probably are not descriptive enough.
  \\
  I consider myself a top-tier horde player, along the likes of accordion,
  marco, and gnostek; my most recent horde achievement at the time of writing
  this is a
  \href{https://www.reddit.com/r/eu4/comments/gh9by2/1531\_oiratgolden\_hordehre\_true\_one\_tag\_wc\_also\_no/}
  {1531 WC as Oirat} in 1.29.6, which is to my knowledge the fastest recorded WC
  during the territorial corruption patches. Given the other horde
  players' inactivities, I think I make a good case for my playstyle to be the
  template to follow when optimizing for rapid expansion.
\end{frame}

\begin{frame}
  \frametitle{Assumptions}
  \begin{itemize}
    \item Optimizing rapid expansion is the objective.
    \item You should have general game sense and basic knowledge -- having done a WC at least once would be helpful.
    \item You should have all DLCs; I make no guarantees whether what I say
      makes sense without certain DLCs.
    \item You should have basic familiarity with hordes.
  \end{itemize}
\end{frame}

\begin{frame}
  \frametitle{Promises}
  In these lectures, I will provide
  \begin{itemize}
    \item The knowledge required to pre-1600 WC -- whether you do it or not
      depends on your willpower, but you will at least be convinced that it is
      possible, and in fact, approachable at least in theory.
    \item General guidelines to optimize expansion
    \item Occasional cat pics
  \end{itemize}
\end{frame}

